Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-07 manuscript.tex
7 updates

When fitting a SN density to the CCF, it is possible at once to retrieve parameters that describe the RV, i.e. the CCF barycenter, the amplitude, sometimes called the CCF contrast, the width, and the asymmetry of the CCF. To estimate the RV, we investigated the use of the mean and the median of the SN density. Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.

>>>>

When fitting a SN density to the CCF, parameters that describe the RV (i.e. the CCF barycenter), the amplitude (sometimes called the CCF contrast), the width, and the asymmetry of the CCF can all be estimated in a single model framework.
For the RV estimator, we investigated the use of the mean and the median of the SN density. 
Then the width is derived using the variance of the SN density (SN FWHM$=2\sqrt{2ln(2)\sigma^2}$) and the asymmetry by using $\gamma$, the skewness parameter of the SN density.
